That’s a Big-Ass Chicken: A Mixed Methods Examination of Urban Backyard Chicken Husbandry

### 2025-03-06 BAC_Manuscript_Final.qmd
testing to render pdf

---
title: "That’s a Big-Ass Chicken: A Mixed Methods Examination of Urban Backyard Chicken Husbandry"
shorttitle: "That's a Big-Ass Chicken"
author:
  - name: Karen Veronica Becerra
    corresponding: true
    orcid: 0009-0006-4967-0955
    email: kvbecerra@Uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Department of Psychology 
        address: 5848 S. University Avenue
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
        id: uchicago
    role:
      - conceptualization
      - formal anlaysis
      - methodology
      - project administration
      - software
      - visualization
      - editing 
  - name: Kristen M. Johnson
    orcid: 0009-0008-3757-5795
    email: kmjohnson25@uchicago.edu 
    affiliations:
      - ref: uchicago
    role:
      - conceptualization
      - data curation
      - methodology
      - project administration
      - software
      - writing
      - editing
  - name: Michael Moroz
    orcid: 0009-0000-9772-0001
    email: mrmoroz@uchicago.edu
    affiliations:
      - ref: uchicago
    role:
      - formal anlaysis
      - software
      - visualization
      - editing
abstract: "This study investigates the growing phenomenon of backyard chicken keeping in urban and suburban environments, a practice that has gained significant momentum amid rising commercial egg prices. Employing a mixed methods approach, we analyzed quantitative data from ______. Concurrently, we conducted thematic analysis of in-depth interviews with backyard chicken owners to explore perceived benefits and challenges. Our findings indicate that while initial setup costs average $487, households recover this investment within 14 months through egg production, with additional benefits including reduced food waste, improved garden soil quality, and reported increases in household well-being. Challenges identified include time commitment (averaging 28 minutes daily), navigating municipal regulations, and managing seasonal variations in productivity. Factor analysis revealed that success factors cluster around three dimensions: appropriate infrastructure, consistent maintenance routines, and community support networks. Ultimately, our results support the hypothesis that the benefits of backyard chicken keeping outweigh the challenges for most practitioners, though successful implementation depends on household-specific variables and community context. This research contributes to growing literature on urban agriculture while providing practical insights for potential chicken keepers, municipal policymakers, and sustainability advocates."
keywords: [chickens, backyard, eggs, pros and cons, bigger is better]
author-note:
  disclosures:
    conflict of interest: The authors have no conflicts of interest to declare.
  financial-support: "This study was supported by a grant from The International Society for Fowl Language."
  gratitude: "The authors are grateful to Eddy the Chicken for her endless inspiration and reluctant support."
impact-statement: "This study illustrates not only how, but also why one should raise big-ass backyard chickens. The results may be used by numerous individuals to convince their domestic partners (such as the second author's husband) to build a backyard coop and give in to the siren squawk of that sweet sweet chicken-raisin' lifestyle."
bibliography: Chickens.bib
format: 
  #apaquarto-docx: default 
  #apaquarto-html: default    # remember to reverse commenting out other formats when turning project in
  apaquarto-pdf: default
floatsintext: true
documentmode: man
donotrepeattitle: true
mainfont: "Times New Roman"
fontsize: 12pt

>>>>

---
output:pdf
title: "That’s a Big-Ass Chicken: A Mixed Methods Examination of Urban Backyard Chicken Husbandry"
shorttitle: "That's a Big-Ass Chicken"
author:
  - name: Karen Veronica Becerra
    corresponding: true
    orcid: 0009-0006-4967-0955
    email: kvbecerra@Uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Department of Psychology 
        address: 5848 S. University Avenue
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
        id: uchicago
    role:
      - conceptualization
      - formal anlaysis
      - methodology
      - project administration
      - software
      - visualization
      - editing 
  - name: Kristen M. Johnson
    orcid: 0009-0008-3757-5795
    email: kmjohnson25@uchicago.edu 
    affiliations:
      - ref: uchicago
    role:
      - conceptualization
      - data curation
      - methodology
      - project administration
      - software
      - writing
      - editing
  - name: Michael Moroz
    orcid: 0009-0000-9772-0001
    email: mrmoroz@uchicago.edu
    affiliations:
      - ref: uchicago
    role:
      - formal anlaysis
      - software
      - visualization
      - editing
abstract: "This study investigates the growing phenomenon of backyard chicken keeping in urban and suburban environments, a practice that has gained significant momentum amid rising commercial egg prices. Employing a mixed methods approach, we analyzed quantitative data from ______. Concurrently, we conducted thematic analysis of in-depth interviews with backyard chicken owners to explore perceived benefits and challenges. Our findings indicate that while initial setup costs average $487, households recover this investment within 14 months through egg production, with additional benefits including reduced food waste, improved garden soil quality, and reported increases in household well-being. Challenges identified include time commitment (averaging 28 minutes daily), navigating municipal regulations, and managing seasonal variations in productivity. Factor analysis revealed that success factors cluster around three dimensions: appropriate infrastructure, consistent maintenance routines, and community support networks. Ultimately, our results support the hypothesis that the benefits of backyard chicken keeping outweigh the challenges for most practitioners, though successful implementation depends on household-specific variables and community context. This research contributes to growing literature on urban agriculture while providing practical insights for potential chicken keepers, municipal policymakers, and sustainability advocates."
keywords: [chickens, backyard, eggs, pros and cons, bigger is better]
author-note:
  disclosures:
    conflict of interest: The authors have no conflicts of interest to declare.
  financial-support: "This study was supported by a grant from The International Society for Fowl Language."
  gratitude: "The authors are grateful to Eddy the Chicken for her endless inspiration and reluctant support."
impact-statement: "This study illustrates not only how, but also why one should raise big-ass backyard chickens. The results may be used by numerous individuals to convince their domestic partners (such as the second author's husband) to build a backyard coop and give in to the siren squawk of that sweet sweet chicken-raisin' lifestyle."
bibliography: Chickens.bib
format: 
  #apaquarto-docx: default 
  #apaquarto-html: default    # remember to reverse commenting out other formats when turning project in
  apaquarto-pdf: default
floatsintext: true
documentmode: man
donotrepeattitle: true
mainfont: "Times New Roman"
fontsize: 12pt
